An Embedding Framework for Consistent Polyhedral Surrogates

### 2019-05-23 neurips-19/poly-embed.tex
Actually inlining Thm 2
tex hacking for space
shrink
section -> paragraph

\subsection{Related works}

The literature on convex surrogates focuses mainly on smooth surrogate losses~\cite{crammer2001algorithmic,bartlett2006convexity,bartlett2008classification, duchi2018multiclass, williamson2016composite, reid2010composite}.
Nevertheless, nonsmooth losses, such as the polyhedral losses we consider, have been proposed and studied for a variety of classification-like problems\cite{yang2018consistency,yu2018lovasz,lapin2015top}.
%\jessiet{Do we want the SVM (Boser) cite?}\raft{Basically anything we talk about in the examples. removed hari from this link since we mention it next}
A notable addition to this literature is~\citet{ramaswamy2018consistent}, who argue that nonsmooth losses may enable dimension reduction of the prediction space (range of the surrogate hypothesis) relative to smooth losses, illustrating this conjecture with a surrogate for \emph{abstain loss} needing only $\log n$ dimensions for $n$ labels, whereas the best known smooth loss needs $n-1$.
Their surrogate is a natural example of an embedding (cf.~Section~\ref{sec:abstain}), and serves as inspiration for our work.

@@

In classification settings with a large number of labels, several authors consider a variant of classification, with the addition of a ``reject'' or \emph{abstain} option.
For example, \citet{ramaswamy2018consistent} study the loss $\ellabs{\alpha} : [n] \cup \{\bot\} \to \reals^\Y_+$ defined by
\begin{align}\label{eq:abstain-discrete}
\ellabs{\alpha}(r)_y = \begin{cases}
0 & r = y\\
\alpha & r = \bot\\
1 & \text{otherwise}
\end{cases}~.
\end{align}
Here, the report $\bot$ corresponds to ``abstaining'' if no label is sufficiently likely, specifically, if no $y\in\Y$ has $p_y \geq 1-\alpha$.
\citet{ramaswamy2018consistent} provide a polyhedral surrogate for $\ellabs{\alpha}$, which we present here for $\alpha=1/2$.
Letting $d = \ceil{\log_2(n)}$ their surrogate is $L_{1/2} : \reals^d \to \reals^\Y_+$ given by
\begin{equation}\label{eq:abstain-surrogate}
L_{1/2}(u)_y = \left(\max_{j \in [d]}B(y)_j u_j + 1\right)_+~,
\end{equation}
where $B:[n]\to\{-1,1\}^d$ is a arbitrary injection; let us assume $n = 2^d$ so that we have a bijection.
Consistency is proven for the following link function,
\begin{equation}\label{eq:abstain-link}
  \psi(u) = \begin{cases}
	\bot & \min_{i \in [d]} |u_i| \leq 1/2\\
	B^{-1}(\sgn(-u)) &\text{otherwise}
  \end{cases}~.
\end{equation}

@@

Surrogates for this problem commonly take reports $u\in\reals^n$, with the link $\psi(u) = \{u_{[1]},\ldots,u_{[k]}\}$, where $x_{[u]}$ is the $i^{th}$ largest component of $u$, with ties broken arbitrarily.
\citet{lapin2015top, lapin2016loss, lapin2018analysis} provide the following convex surrogate loss for this problem, which \citet{yang2018consistency} show to be inconsistent:%
\footnote{Yang and Koyejo also introduce a consistent surrogate, but it is non-convex.}
\begin{align}\label{eq:L-2-surrogate}
  L'(u)_y := \left( \frac{1}{k} \sum_{i=1}^k (u + \ones - e_y)_{[i]} - u_y \right)_+~,
\end{align}
where $e_y$ is $1$ in component $y$ and 0 elsewhere.

>>>>

\paragraph{Related works.}
The literature on convex surrogates focuses mainly on smooth surrogate losses~\cite{crammer2001algorithmic,bartlett2006convexity,bartlett2008classification, duchi2018multiclass, williamson2016composite, reid2010composite}.
Nevertheless, nonsmooth losses, such as the polyhedral losses we consider, have been proposed and studied for a variety of classification-like problems\cite{yang2018consistency,yu2018lovasz,lapin2015top}.
%\jessiet{Do we want the SVM (Boser) cite?}\raft{Basically anything we talk about in the examples. removed hari from this link since we mention it next}
A notable addition to this literature is~\citet{ramaswamy2018consistent}, who argue that nonsmooth losses may enable dimension reduction of the prediction space (range of the surrogate hypothesis) relative to smooth losses, illustrating this conjecture with a surrogate for \emph{abstain loss} needing only $\log n$ dimensions for $n$ labels, whereas the best known smooth loss needs $n-1$.
Their surrogate is a natural example of an embedding (cf.~Section~\ref{sec:abstain}), and serves as inspiration for our work.

@@

In classification settings with a large number of labels, several authors consider a variant of classification, with the addition of a ``reject'' or \emph{abstain} option.
For example, \citet{ramaswamy2018consistent} study the loss $\ellabs{\alpha} : [n] \cup \{\bot\} \to \reals^\Y_+$ defined by
%\begin{align}\label{eq:abstain-discrete}
$\ellabs{\alpha}(r)_y = \begin{cases}
0 & r = y\\
\alpha & r = \bot\\
1 & \text{otherwise}
\end{cases}~.$
%\end{align}
Here, the report $\bot$ corresponds to ``abstaining'' if no label is sufficiently likely, specifically, if no $y\in\Y$ has $p_y \geq 1-\alpha$.
\citet{ramaswamy2018consistent} provide a polyhedral surrogate for $\ellabs{\alpha}$, which we present here for $\alpha=1/2$.
Letting $d = \ceil{\log_2(n)}$ their surrogate is $L_{1/2} : \reals^d \to \reals^\Y_+$ given by
\begin{equation}\label{eq:abstain-surrogate}
L_{1/2}(u)_y = \left(\max_{j \in [d]}B(y)_j u_j + 1\right)_+~,
\end{equation}
where $B:[n]\to\{-1,1\}^d$ is a arbitrary injection; let us assume $n = 2^d$ so that we have a bijection.
Consistency is proven for the following link function,
\begin{equation}\label{eq:abstain-link}
  \psi(u) = \begin{cases}
	\bot & \min_{i \in [d]} |u_i| \leq 1/2\\
	B^{-1}(\sgn(-u)) &\text{otherwise}
  \end{cases}~.
\end{equation}

@@

Surrogates for this problem commonly take reports $u\in\reals^n$, with the link $\psi(u) = \{u_{[1]},\ldots,u_{[k]}\}$, where $x_{[u]}$ is the $i^{th}$ largest component of $u$, with ties broken arbitrarily.
\citet{lapin2015top, lapin2016loss, lapin2018analysis} provide the following convex surrogate loss for this problem, which \citet{yang2018consistency} show to be inconsistent:%
\footnote{Yang and Koyejo also introduce a consistent surrogate, but it is non-convex.}
\begin{align}\label{eq:L-2-surrogate}
  L'(u)_y := \left( \tfrac{1}{k} \textstyle\sum_{i=1}^k (u + \ones - e_y)_{[i]} - u_y \right)_+~,
\end{align}
where $e_y$ is $1$ in component $y$ and 0 elsewhere.
